---
title: "About"
output: distill::distill_article
  toc: TRUE
site: distill::distill_website
---


```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, knitr)
```

### Caveats

Some points that should be borne in mind when browsing the stats on this site. 

- All gambit-related stats in the season reports are likely to be wrong. That's because they're based on a woefully incomplete list of gambits that doesn't even include the Halloween Gambit. This needs to be fixed. One day, it will be. Sorry, Scribbles.
- The new match summary reports don't have a timestamp on them, but in case it wasn't obvious, they only capture the outcome of games and matches at the time they were made. The results of a game can be revised after it's played -- eg if a player is booted from the league for violating Lichess's Terms of Service -- and when this happens, this can obviously affect the outcome of a match. 


### Acknowledgements {#acknowledgements}

```{r}
credits <- c("glbert", "ErinYu", "lc91", "gingersquirrelnuts", "Chewbacca_Defense", 
             "MrScribbles", "IsaVulpes", "Ecclesiastic", "alen111", "Tranzoo", "Silkthewanderer", "Lou-E", "gavalanche20")

credits <- stringr::str_c(sort(credits), collapse = ", ")
```


Thanks to the following Lichess4545 members for providing helpful advice, suggestions and inspiration along the way: `r credits`.

The quotes in the footer come from a list of reasons to play in the 4545 league that Tranzoo recently compiled, with contributions from gigantaure, M0r1, unclevinny, seb32, KnightFury21, kostasvsl, mojomoe and Impaired.


### Contact {#contact}

Please use the form below to provide any comments, suggestions or bug reports.

```{=html}
<form method="post" action="https://forms.un-static.com/forms/c65e8c7acaf8b132767fee1fba923d3d07b959c5">
  <div class="form-group row">
    <label for="name" class="col-4 col-form-label">Name</label>
    <div class="col-8">
      <div class="input-group">
        <div class="input-group-addon">
          <i class="fa fa-user"></i>
        </div>
        <input id="name" name="name" placeholder="Please enter your name" type="text" required="required" class="form-control">
      </div>
    </div>
  </div>
  <div class="form-group row">
    <label for="email" class="col-4 col-form-label">E-mail address (optional)</label>
    <div class="col-8">
      <div class="input-group">
        <div class="input-group-addon">
          <i class="fa fa-envelope"></i>
        </div>
        <input id="email" name="email" placeholder="Your e-mail address" type="text" class="form-control">
      </div>
    </div>
  </div>
  <div class="form-group row">
    <label for="message" class="col-4 col-form-label">Message</label>
    <div class="col-8">
      <textarea id="message" name="message" cols="40" rows="10" required="required" class="form-control"></textarea>
    </div>
  </div>
  <div class="form-group row">
    <div class="offset-4 col-8">
      <button name="submit" type="submit" class="button">Send</button>
    </div>
  </div>
</form>
<div align="center">
  <p><small>(Powered by <a rel="nofollow" href="https://un-static.com/">Un-static Forms</a>)</small></p>
</div>
```

