---
title: "Lichess4545 stats homepage"
output: md_document
date: "Last updated: `r format(Sys.time(), '%B %Y')`"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, knitr)

```


This page hosts detailed statistical reports on all previous [Lichess4545](https://www.lichess4545.com/team4545/) and [LoneWolf](https://www.lichess4545.com/lonewolf/) seasons.

For the uninitiated, these are two popular online chess leagues that have been running since 2015. They're regularly recommended by top players like IM John Bartholomew -- see [here](https://www.youtube.com/watch?v=8gBGcOEvsy4&t=1296). You can find out more at https://www.lichess4545.com/.

---

[All-time records](#alltime) | [Stats/awards by league/season](#season-stats) | [Updates](#updates) | [Acknowledgements](#acknowledgements) | [Contact](#contact)

---

## All time records {#alltime}

[All time records](https://rahulan-c.github.io/lichess4545-stats/reports/alltime_stats.html)

## Stats and awards by league/season {#season-stats} 

```{r season_reports_tbl}

# Identify all seasons for which stats reports have been compiled 

# 4545
completed_4545 <- list.files(path = "reports/", pattern = "^stats_4545(.*)\\.html$") 
any_4545 <- ifelse(length(completed_4545) > 0, T, F)
if(length(completed_4545) > 0){
  completed_4545 <- completed_4545 %>% 
    str_remove_all("stats_4545_s") %>% 
    str_remove_all("\\.html") %>% 
    sort(decreasing = T) %>% 
    paste0("[Season ", ., "]", "(https://rahulan-c.github.io/lichess4545-stats/reports/stats_4545_s", ., ".html)")
}

# LW Open
completed_lwopen <- list.files(path = "reports/", pattern = "^stats_lwopen(.*)\\.html$")
any_lwopen <- ifelse(length(completed_lwopen) > 0, T, F)
if(length(completed_lwopen) > 0){
  completed_lwopen <- completed_lwopen %>% 
    str_remove_all("stats_lwopen_s") %>% 
    str_remove_all("\\.html") %>% 
    sort(decreasing = T) %>% 
    paste0("[Season ", ., "]", "(https://rahulan-c.github.io/lichess4545-stats/reports/stats_lwopen_s", ., ".html)")
}

# LW U1800
completed_lwu1800 <- list.files(path = "reports/", pattern = "^stats_lwu1800(.*)\\.html$")
any_lwu1800 <- ifelse(length(completed_lwu1800) > 0, T, F)
if(length(completed_lwu1800) > 0){
 completed_lwu1800 <- completed_lwu1800 %>%  
   str_remove_all("stats_lwu1800_s") %>% 
   str_remove_all("\\.html") %>% 
   sort(decreasing = T) %>% 
   paste0("[Season ", ., "]", "(https://rahulan-c.github.io/lichess4545-stats/reports/stats_lwu1800_s", ., ".html)")
}

# Make sure all completed season vectors are the same length
most_completed <- max(c(length(completed_4545), 
                      length(completed_lwopen), 
                      length(completed_lwu1800)))

if(length(completed_4545) < most_completed){
  completed_4545 <- c(completed_4545, rep("", most_completed - length(completed_4545)))
}

if(length(completed_lwopen) < most_completed){
  completed_lwopen <- c(completed_lwopen, rep("", most_completed - length(completed_lwopen)))
}

if(length(completed_lwu1800) < most_completed){
  completed_lwu1800 <- c(completed_lwu1800, rep("", most_completed - length(completed_lwu1800)))
}

# Make league cols empty if there are no completed seasons
if(any_4545 == F){completed_4545 <- rep("", most_completed)}
if(any_lwopen == F){completed_lwopen <- rep("", most_completed)}
if(any_lwu1800 == F){completed_lwu1800 <- rep("", most_completed)}

# Construct and show table of league reports by season
completed <- tibble("team4545" = completed_4545,
                    "lwopen" = completed_lwopen,
                    "lwu1800" = completed_lwu1800)
knitr::kable(completed, format = "simple", col.names = c("Lichess4545 League", "Lichess LoneWolf (Open)", "Lichess LoneWolf (U1800)"))

```

## Updates {#updates}

### Recent updates

- 2021-08-16: added an initial all-time stats page with a combined table of award winners across all leagues/seasons
- 2021-08-15: updated home page with new sections and contact form.
- 2021-08-09: amended the treatment of banned players; revised some plots and tables; and added two new awards (Rookie and Egalitarian), season forfeit rates, and several explanatory footnotes.
- 2021-08-04: updates; first full set of season reports published.
- 2021-07-30: first reports published.

### Future updates

Here are some planned updates that I'm either actively working on or have on my 'to do' list. Many of them have been suggested by other Lichess4545 members. If there's something you'd like to see, please get in touch using the contact form below. Nothing is impossible...except maybe identifying piece sacrifices :)

**Planned updates to season stats**
 
- Showing positions from games
- Identifying game(s) that were last to deviate from "theory" (aka the Lichess masters DB) `in progress`
- Visualising important team matches (or matches that went to the wire) `in progress`
- Showing players that ended up with more time than they began with
- Stats by endgame
- Improving gambit-related stats

**Other planned updates** 

- All-time 4545 and LoneWolf stats `under construction - see above`
- Presenting stats for other Lichess4545 community leagues (eg Rapid Battle, Series...)

## Acknowledgements {#acknowledgements}

```{r}
credits <- c("glbert", "ErinYu", "lc91", "gingersquirrelnuts", "Chewbacca_Defense", 
             "MrScribbles", "IsaVulpes", "Ecclesiastic", "alen111", "Tranzoo", "Silkthewanderer", "Lou-E", "gavalanche20")

credits <- str_c(sort(credits), collapse = ", ")
```


Thanks to the following Lichess4545 members for providing helpful advice, suggestions and inspiration along the way: `r credits`.


## Contact me {#contact}

Please use the form below to provide any comments, suggestions or bug reports.

```{=html}
<form method="post" action="https://forms.un-static.com/forms/c65e8c7acaf8b132767fee1fba923d3d07b959c5">
  <div class="form-group row">
    <label for="name" class="col-4 col-form-label">Name</label>
    <div class="col-8">
      <div class="input-group">
        <div class="input-group-addon">
          <i class="fa fa-user"></i>
        </div>
        <input id="name" name="name" placeholder="Please enter your name" type="text" required="required" class="form-control">
      </div>
    </div>
  </div>
  <div class="form-group row">
    <label for="email" class="col-4 col-form-label">E-mail address (optional)</label>
    <div class="col-8">
      <div class="input-group">
        <div class="input-group-addon">
          <i class="fa fa-envelope"></i>
        </div>
        <input id="email" name="email" placeholder="Your e-mail address" type="text" class="form-control">
      </div>
    </div>
  </div>
  <div class="form-group row">
    <label for="message" class="col-4 col-form-label">Message</label>
    <div class="col-8">
      <textarea id="message" name="message" cols="40" rows="10" required="required" class="form-control"></textarea>
    </div>
  </div>
  <div class="form-group row">
    <div class="offset-4 col-8">
      <button name="submit" type="submit" class="button">Send</button>
    </div>
  </div>
</form>
<div align="center">
  <p><small>(Powered by <a rel="nofollow" href="https://un-static.com/">Un-static Forms</a>)</small></p>
</div>
```



*`r paste0("Site last updated at ", format(Sys.time(), '%X %Z'), " on ", format(Sys.time(), '%a %d %b %Y'))`.*
