---
title: "Players by country/continent"
description: |
  Where do league players come from?
date: "2022-01-05"
output: 
  distill::distill_article:
    code_folding: true
site: distill::distill_website
---

Here are some rough estimates of league players by country and continent, based on all classical league games played to date (January 2022). They're purely based on the national flags shown on league members' Lichess profile pages, which means that they definitely won't be perfect, since many players don't have a flag on their profile page (so they're excluded), and others prefer to display a non-national flag (so they're also excluded). Moreover, players can show any flag they want...which may well explain some of the countries listed in the results. `r emo::ji("laugh")`


```{r}

# ==== PRELIMINARIES ==========================================================

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, data.table, here, httr, jsonlite, rmarkdown,
               rvest, utf8, tmap, sf)

token <- Sys.getenv("LICHESS_TOKEN") # Lichess API token


# ==== LOAD/TIDY SUPPORTING DATASETS ==========================================

# --- Country lookup data -----------------------------------------------------
countrycodes_url <-  "https://gist.githubusercontent.com/stevewithington/20a69c0b6d2ff846ea5d35e5fc47f26c/raw/13716ceb2f22b5643ce5e7039643c86a0e0c6da6/country-and-continent-codes-list-csv.csv"
country_data <- readr::read_csv(countrycodes_url) 

# Tidy duplicate records (dual continent countries)
country_data <- country_data %>% 
  filter(!((Country_Name == "Azerbaijan, Republic of") & (Continent_Name == "Asia")),
         !((Country_Name == "Armenia, Republic of") & (Continent_Name == "Asia")),
         !((Country_Name == "Cyprus, Republic of") & (Continent_Name == "Asia")),
         !((Country_Name == "Georgia") & (Continent_Name == "Asia")),
         !((Country_Name == "Kazakhstan, Republic of") & (Continent_Name == "Asia")),
         !((Country_Name == "United States Minor Outlying Islands") & (Continent_Name == "North America")),
         !((Country_Name == "Russian Federation") & (Continent_Name == "Asia")),
         !((Country_Name == "Turkey, Republic of") & (Continent_Name == "Asia"))
  )

# Add Kosovo (missing due to being partially recognised)
country_data <- country_data %>% 
  add_row(Continent_Name = "Europe",
            Continent_Code = "EU",
            Country_Name = "Kosovo, Republic of",
            Two_Letter_Country_Code = "XK",
            Three_Letter_Country_Code = NA,
            Country_Number = NA)


# ---- World data (for map) ---------------------------------------------------
data("World")
World %>% mutate(across(where(is.factor), as.character)) -> World

# ---- League games data ------------------------------------------------------

# Using all 4545, LoneWolf and Series games played to date
games <- readRDS(paste0(here::here(), "/data/allgames_teamlwseries.rds"))
games <- tibble::as_tibble(games)

# ==== GET PLAYER PROFILE DATA ================================================

# Get user IDs of all players in the season games data
player_ids <- rbind(tibble("player" = games$white),
                    tibble("player" = games$black)) %>% 
  dplyr::select(player) %>% 
  dplyr::distinct() %>% 
  dplyr::arrange(player) %>% 
  dplyr::pull()

# Request public profile data for all players
# Max 300 per request
all_player_ids <- split(player_ids, ceiling(seq_along(player_ids)/300))
all_profiles <- list()
for(l in seq(1:length(all_player_ids))){
  batch_ids <- all_player_ids[[l]] %>% stringr::str_c(collapse = ",")
  profiles <- httr::POST(
    url = "https://lichess.org",
    path = paste0("/api/users"),
    body = batch_ids,
    httr::add_headers(`Authorization` = sprintf("Bearer %s", token)),
    accept("application/json"))
  
  profiles <- profiles %>% 
    httr::content("text", encoding = stringi::stri_enc_detect(httr::content(profiles, "raw"))[[1]][1,1]) %>% 
    jsonlite::fromJSON()
  
  # Extract relevant info
  player_profiles <- tibble("id" = profiles$id,
                            "username" = profiles$username,
                            "country" = profiles$profile$country,
                            "location" = profiles$profile$location,
                            "language" = profiles$language,
                            "rating_classical" = profiles$perfs$classical$rating)
  
  all_profiles[[l]] <- player_profiles
  # print(paste0("Requested batch ", l))
  if(l != length(all_player_ids)){Sys.sleep(0.5)}
}

# Collate obtained profile datasets
player_profiles <- data.table::rbindlist(all_profiles)


# ==== COMPUTE PLAYERS BY COUNTRY AND CONTINENT ===============================

# Tidy player country data
players_by_country <- player_profiles %>% 
  dplyr::filter(!(is.na(country))) %>% 
  tibble::as_tibble()

# 1) Make GB-based players have the same country code
players_by_country$country[players_by_country$country == "GB-ENG"] <- "GB"
players_by_country$country[players_by_country$country == "GB-WLS"] <- "GB"
players_by_country$country[players_by_country$country == "GB-SCT"] <- "GB"
players_by_country$country[players_by_country$country == "GB-NIR"] <- "GB"

# 2) Fix players with Belarus, Catalonia and Quebec flags
players_by_country$country[players_by_country$country == "_belarus-wrw"] <- "BY"
players_by_country$country[players_by_country$country == "ES-CT"] <- "ES"
players_by_country$country[players_by_country$country == "CA-QC"] <- "CA"

# 3) Exclude players with missing or non-country flags  
players_by_country <- players_by_country %>% 
  dplyr::filter(!(country %in% c("_lichess", "_rainbow", "_pirate", "_earth", 
                          "_united-nations", "AQ"))) %>% 
  dplyr::filter(!(is.na(country))) %>% 
  tibble::as_tibble()

# 4) Apply manual edits for players with insufficient/wrong/known info
# DETAILS NOT SHOWN
```



```{r, include = FALSE}
# Manual edits to player/country data (NOT SHOWN)
manual_changes <- tibble::tibble(
  id = c("jwwells42", 
         "hausierer",
         "howhorseymoves",
         "lou-e",
         "thibault",
         "gandalftheperiwinkle",
         "jaivl",
         "mini_karpov",
         "nyave",
         "buddhastalin",
         "hamhamslam",
         "hemligagent",
         "sgis",
         "ssyx",
         "mrmoo",
         "salty-8k",
         "scott9315",
         "khasi1596",
         "lambdac",
         "leasy",
         "lvdr",
         "neilwang",
         "qveen_sacrifice",
         "roso97",
         "sasha-nbo",
         "wo_schrodinger",
         "exirk",
         "adande1",
         "glbert",
         "gingersquirrelnuts",
         "jacade",
         "landypjy",
         "the_wayward_prince",
         "pulsar512b",
         "matt_chess_play",
         "moistvonlipwig",
         "zeebu"),
  
  country = c("US", 
              "DE",
              "ZA",
              "GB",
              "FR",
              "US",
              "ES",
              "VN",
              "US",
              "US",
              "US",
              "SE",
              "CH",
              "GB",
              "US",
              "US",
              "US",
              "US",
              "US",
              "DE",
              "FI",
              "US",
              "US",
              "CH",
              "GB",
              "CA",
              "US",
              "US",
              "AT",
              "GB",
              "DE",
              "US",
              "US",
              "US",
              "CH",
              "DE",
              "US")
)

# Apply manual changes
for (r in seq(1:nrow(manual_changes))){
  players_by_country$country[players_by_country$id == manual_changes$id[r]] <- manual_changes$country[r]
}

# Remove selected players from data 
players_by_country <- players_by_country %>% 
  filter(id != "erinyu") %>% 
  filter(id != "stubenfisch") %>% 
  filter(id != "ipr")
```

## Players by continent

```{r}

# After the data has been tidied, merge the the profile and country data
players_by_country <- left_join(players_by_country, country_data, by = c("country" = "Two_Letter_Country_Code"))

# Shorten some of the country names (eg "Armenia, Republic of" -> "Armenia")
players_by_country <- players_by_country %>% 
  mutate(country_name_2 = ifelse(str_detect(Country_Name, ","), str_sub(Country_Name, 1, str_locate(Country_Name, ",") - 1), Country_Name))

# Shorten the United Kingdom label
players_by_country$country_name_2[players_by_country$country_name_2 == "United Kingdom of Great Britain & Northern Ireland"] <- "United Kingdom"

# Add continent data for players with EU flags
players_by_country$Continent_Name[players_by_country$country == "EU"] <- "Europe"
eu_players <- length(players_by_country$Continent_Name[players_by_country$country == "EU"])


# Group and order players by continent (including 'EU' players)
summary_continent <- players_by_country %>% 
  group_by(Continent_Name) %>% 
  summarise(players = n()) %>% 
  mutate(perc = round((players / sum(players)) * 100, 1)) %>% 
  arrange(desc(players)) %>% 
  rename("continent" = Continent_Name)
paged_table(summary_continent)
```

## Players by country

```{r}

# Group and order players by country
summary_country <- players_by_country %>% 
  filter(!(country == "EU")) %>% # exclude players with EU flags
  group_by(country_name_2) %>% 
  summarise(players = n()) %>% 
  mutate(perc = round((players / sum(players)) * 100, 1)) %>% 
  arrange(desc(players)) %>% 
  rename("country" = country_name_2)
paged_table(summary_country)

```

## Map

```{r}

# Revise country names in World data to match those in players data
World$name[World$name == "United States"] <- "United States of America"
World$name[World$name == "Russia"] <- "Russian Federation"
World$name[World$name == "Slovakia"] <- "Slovakia (Slovak Republic)"
World$name[World$name == "Czech Rep."] <- "Czech Republic"
World$name[World$name == "Palestine"] <- "Palestinian Territory"

# Note: the 'World' data doesn't have records for some countries (eg Singapore,
# Kosovo) so slightly fewer players will be shown on the map vs the table

# Create map dataset
players_by_country_map <- left_join(World, summary_country, by = c("name" = "country"))
players_by_country_map <- players_by_country_map %>% 
  select(name, players, perc, continent, geometry) %>% 
  st_as_sf()

players_by_country_map <-  st_transform(players_by_country_map, crs = "+proj=moll")


# Make/show world map
world_map <- tm_shape(players_by_country_map) + 
  tm_polygons("players", 
              title = "Players by country", 
              colorNA = "#b5b5b5",
              style = "jenks",
              palette = "YlGn") +
  tm_layout(earth.boundary = c(-180, -88, 180, 88),
            frame = F,
            legend.position = c("left", "bottom")) +
  tm_format("World_wide")
world_map
```

